Parsing Postfix log files

### 2007-05-29 doc/logparser.tex
Added new graph - percentage increase of shuffled over normal and reversed over normal. Removed file sizes and lines from normal vs shuffled vs reversed. Appropriate Makefile changes, plus minor improvements. Documented averaging of run times and discarding of first run.

        For efficiency the keywords are expanded and every rule's regex is
        compiled before attempting to parse the log file --- otherwise each
        regex would be recompiled each time it was used, resulting in a
        large, data dependent slowdown.  Graph \ref{normal regex vs discard
        regex} shows execution times gathered over 93 log files, with and
        without caching the regex; also shown on the graph are the file
        sizes and number of lines in each file.  Graph \ref{normal regex vs
        disarded regex factor} shows the percentage execution time increase
        when not caching each regex.  Logging to the database was disabled
        for the test runs.

@@

    \item [rule\_order] This is an efficiency measure.  This counter is
        maintained for every rule and incremented each time the rule
        successfully matches.  At the start of each run the program sorts
        the rules in descending rule\_order, and at the end of the run
        updates every rule's rule\_order.  Assuming that the distribution
        of log lines is reasonably consistent, rules matching more commonly
        occurring log lines will be tried before rules matching less
        commonly occurring log lines, lowering the program's execution
        time.
\ref{normal vs shuffled vs reversed ordering}

        Averaged over 10 test runs:

            \item [Ascending order (best):] run time was 56.684 seconds,
                standard deviation was 0.29 seconds.

            \item [Descending order (worst):] run time was 64.037
                seconds (12.97\% slower), standard deviation was 0.16
                seconds.

            \item [Shuffled order:] run time was 57.19 seconds
                (0.89\% slower), standard deviation was 0.95 seconds.

        XXX RERUN OVER MORE LOG FILES

        XXX RERUN AGAIN ONCE POSTFIX 2.3 RULES HAVE BEEN ADDED TO SEE WHAT
        THE DIFFERENCE IS.  THERE ARE 110 POSTFIX 2.2 RULES AS OF
        2007/04/18

        Logging to the database was disabled for the test runs.

        It is hoped that this will prove to have greater effectiveness as
        the number of rules grows; currently the effect is negligible,
        particularly in comparison to compiling each regex once.

@@

>>>>

        For efficiency the keywords are expanded and every rule's regex is
        compiled before attempting to parse the log file --- otherwise each
        regex would be recompiled each time it was used, resulting in a
        large, data dependent slowdown.  Graph \ref{normal regex vs discard
        regex} shows execution times gathered over 93 log files, with and
        without caching the regex; also shown on the graph are the file
        sizes and number of lines in each file.  Graph \ref{normal regex vs
        disarded regex factor} shows the percentage execution time increase
        when not caching each regex.  Each log file was parsed 10 times,
        the first run discarded and the remaining 9 runs averaged.  Logging
        to the database was disabled for the test runs.

@@

    \item [rule\_order] This is an efficiency measure.  This counter is
        maintained for every rule and incremented each time the rule
        successfully matches.  At the start of each run the program sorts
        the rules in descending rule\_order, and at the end of the run
        updates every rule's rule\_order.  Assuming that the distribution
        of log lines is reasonably consistent between log files, rules
        matching more commonly occurring log lines will be tried before
        rules matching less commonly occurring log lines, lowering the
        program's execution time.  Graph \ref{normal vs shuffled vs
        reversed ordering} plots the execution time over 93 log files for
        normal, shuffle and reverse ordering.  Graph \ref{normal vs
        shuffled vs reversed ordering factor} shows the percentage
        execution time increase for shuffled and reversed over normal.
        Each log file was parsed 10 times, the first run discarded and the
        remaining 9 runs averaged.  Logging to the database was disabled
        for the test runs.

        It is hoped that this will prove to have greater effectiveness as
        the number of rules grows; currently the effect is negligible
        in comparison to caching each compiled regex, but it still provides
        approximately a 10\% performance increase.

@@

\subsection{Percentage increase of shuffled over normal and reversed over normal}
\label{normal vs shuffled vs reversed ordering factor}
\includegraphics{plot-normal-shuffle-reverse-factor.ps}
